%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Nishanth}{D Aluhonnu}{

\
\href{nishanthdilip@yahoo.co.in}{nishanthdilip@yahoo.co.in}\\
\
\href{mailto:nishaqnthdilip@gmail.com}{nishaqnthdilip@gmail.com} | +91 9036885867
}
\
\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{about me}
\descript{i am a motivated person capable of working under pressure in a team as well as an individual contributor. i like learning new technologies. in my leisure, i engage in gaming and listen to music.}
\
\sectionsep


\section{Education} 

\descript{R.V College of Engineering}
%\subsection{R.V COLLEGE OF ENGINEERING}
Electronics and Communication Engineering\\
\location{ Cum. GPA: 8.07/10.0(4 semesters)}
\location{2016-2020| Bangalore, India}
    \
\sectionsep

%\subsection{}
\descript{Deeksha Center for Learning}
STATE-XII , PCMC\\
\location{ PCM Percentage: 96.0\%}
\location{Overall Percentage: 88.5\%}
\location{Grad. June 2016 | Bangalore, India}
\
\sectionsep

\descript{St. Paul's English School}
10th Grade , Computer Appln.\\
\location{Overall Percentage: 94.5\%}
\location{Centum in Computer Applications}
\location{Grad. May 2014 | Bangalore, India}
\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/nishu88}{\custombold{nishu88}} \\
LinkedIn://  \href{https://www.linkedin.com/in/nishanth-d-aluhonnu-a3687712a/}{\custombold{nishanth-d-aluhonnu}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%Unix Tools and Scripting \\
%\sectionsep%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 1000 lines:}
Python \textbullet{} Java \textbullet{}   C \textbullet{} C++\\

\location{Familiar:}
 \textbullet{} Android Studio \textbullet{} HTML \\ \textbullet{} MySQL \textbullet{} MATLAB \textbullet{} JavaScript\\ \textbullet{} CSS \textbullet{} Git \textbullet{} \LaTeX
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}


{\href{http://tmsindia.co.in/}{\runsubsection{The Mathitis Society}}}
\descript{| Cloud Computing Intern }
\location{ May 2017 – June 2017 |Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item 1 major Cloud Computing project, Related to EsXi Host and Nic Teaming.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Website Development}
\descript{| for Coding Club RVCE (RVCC)}
\location{August,2018 | Bangalore}
\begin{tightemize}
\item \location{codingclub.rvce.in/}
\end{tightemize}
\runsubsection{Cloud computing}
\descript{| as part of {\href{https://www.microsoft.com/en-in/learning/mta-certification.aspx}{MTA Certification}}}
\location{June,2017 | Bangalore}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
\begin{tightemize}
\item Worked on 4 mini projects related to AdHoc Network, Subnetting, \\
iSCSI target,ESXi host, vSphere.
\end{tightemize}



\sectionsep


%\descript{ Head Undergraduate Researcher}
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
%\sectionsep


\section{Extra-Curricular Activities} 
\
\begin{tightemize}

\item \location{Currently part of Coding Club, RVCE (2017-present).}
\item \location{Participated in an overnight Business Marathon Competition as part of {\href{http://www.rvecell.com/}{ESUMMIT-18.}} }
\item \location{Part of organizing {\href{https://en.wikipedia.org/wiki/Under_the_Peepal_Tree}{UTPT}} as part of {\href{http://www.rvquizcorp.com/}{RV Quiz Corp}} in 8th Mile,2017.}
\item \location{Attended a App development workshop in RV conducted by {\href{https://www.sahajsoft.com}{Sahaj Soft.}} }
\item \location{Digital and Sponsorship Committee member of the organizing team in DCFL for ICUBE-2015. }
\item \location{Part of the school Volley ball team in 10th grade.}
\item \location{18 months of Taekwondo training in school.}

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\
\begin{tightemize}
\item \location{Finalist in an overnight hackathon conducted by Curl Analytics at Techathlon 2k18, RVCE (October 2018).}
\item \location{Secured 1st place in Gazing with ML competition as part of Phaseshift 2k18 at BMSIT (September 2018).}
\item \location{Secured 2nd place in Reverse Coding Competition conducted by IIT Madras as a part of SHAASTRA (2017).}
\item \location{Secured 3rd place in Code Wars 2017 conducted by Coding Club, RVCE (2017).}
\item \location{Got certified in Cloud Fundamentals as part of Microsoft Technology Associate Certification with a aggregate of 89.}
\item \location{Consolidation prize in Vedic Mathematics in school (2012).}
\item \location{Secured 3rd place in school in National Cyber Olympiad (2012).}

\end{tightemize}

\sectionsep

\section{Certificate Links} 
\
\begin{tightemize}
\item \location{{\href{https://drive.google.com/open?id=1equ39yaBeJvaq0I8pr9w5fDY6oMgZU9G}{MTA(Microsoft Technical Associate) Certification}}}

\item \location{{\href{https://drive.google.com/open?id=1M8XJQhCBhAl57ZJxw7HyLlj0y_OC2ry4}{Mathitis Society Internship Letter}}}

\item \location{{\href{https://drive.google.com/open?id=1q58hVyelbtOPLD53ik3N8zj2TC8Lk6T0}{NPTEL Certification-Programming, Data Structures and Algorithms using Python }}}

\item \location{{\href{https://drive.google.com/open?id=1Y99HDjsKxAptFbGh62n0XAAbqDxbMFcX}{NPTEL Certification-Introduction to Modern Application Development by HASURA and IIT MADRAS}}}
\end{tightemize}

\sectionsep
\end{minipage} 
\end{document}  \documentclass[]{article}